% !TEX root = ../main.tex
%

\vspace*{\fill}
\begin{center}
	Copyright~\copyright~\thesisDate,~\thesisName. \\ All Rights Reserved.
\end{center}
\vspace*{\fill}

\pagebreak

\addchap*{Statement by Author}

This thesis/dissertation has been submitted in partial fulfillment of requirements for an advanced degree at the Villanova University.

The data presented herein were collected as part of a research initiative by Villanova University's Center for Resilient Water Systems (VCRWS) under a grant funded by the Pennsylvania Department of Transportation (PennDOT). These data are to be considered preliminary, and may not be used elsewhere except with explicit written permission from PennDOT or VCRWS. PennDOT and VCRWS make no guarantees as to the integrity of these data, which are provided for informational purposes only and are subject to change upon further review.

The opinions presented in this publication are those of the author and do not necessarily express the opinions of the Pennsylvania Department of Transportation or AECOM. Reference in this report to any commercial product, process, or service, or the use of any trade, firm, or corporation name is for general informational purposes only and does not constitute an endorsement or certification of any kind by the author. This project is a research initiative of the Villanova Center for Resilient Water Systems.

Brief quotations from this thesis/dissertation are allowable without special permission, provided that accurate acknowledgment of source is made. Requests for permission for extended quotation from or reproduction of this manuscript in whole or in part may be granted by the head of the major department or the Associate Dean for Graduate Studies and Research of the College of Engineering when in his or her judgment the proposed use of the material is in the interests of scholarship. In all other instances, however, permission must be obtained from the author.

\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\addchap*{Acknowledgement}
\label{sec:acknowledgement}

This thesis is a result of my studies at Villanova University and my research as a member of the Center for Resilient Water Systems' PennDOT Hydrology Team. I would like to thank my advisors, Dr.~Robert~Traver, Dr.~Bridget~Wadzuk, and Dr.~Gerald~Zaremba, for their endless support, for sharing their wealth of knowledge and experience, and for entertaining my continuous requests to try new things. Madhat Fares, Danielle Galloway, Shaelynn Heffernan, and Matina Shakya, my fellow graduate students, made field work a breeze and provided many hours of troubleshooting, laughs, bouncing ideas around, and more troubleshooting. The Pennsylvania Department of Transportation and AECOM's partnership were key in inspiring, funding, and critiquing our work, and I am forever grateful for their support. Last, but certainly not least, thank you to my family for providing a rich educational background and my friends for their encouragement and support along the way.
